---
title: "R Notebook"
output: html_notebook
---

```{r}
library(stm)
library(tm)
library(tidyverse)
```
# Load the data
Keep only the states which passed an RPS at some point (this is required to plot the years since enactment -- the $\texttt{STM}$ package can't estimate effects with missing covariates). Remove duplicated paragraphs. If the $\texttt{reduction_rate}$ is null, set it to zero. This is a temporary fix to deal with missing covariate data.  Process the text by removing stopwords, numbers and punctuation, and create STM-usable output.
```{r}
data <- read.csv("document_sample.csv")
```


```{r}
processed <- textProcessor(data$text, metadata = data, stem = T)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
docs <- out$documents
vocab <- out$vocab
meta <- out$meta
stm.50 <- stm(docs, vocab, 50, data = meta)
```


```{r}
labels <- labelTopics(stm.50, n = 10)
write.csv(labels$prob, "topiclabels.csv")
write.csv(stm.50$theta, "topicproportions.csv")
```

```{r}
library(boot)
library(lubridate)

boot_fn <- function(fitdata, indices) {
  d <- fitdata[indices,]
  d <- d[order(d$x),]
  n = nrow(d)
  k <- min(ceiling(n/10), n/2)  # Window size
  kernel <- c(dnorm(seq(0, 3, length.out=k)))
  kernel <- c(kernel, rep(0, n - 2*length(kernel) + 1), rev(kernel[-1]))
  kernel <- kernel / sum(kernel)
  y <- Re(convolve(d$y, kernel))
  return(y)
}

moving_window <- function(model, t, years, ci) {
  o <- order(years)
  years <- years[o]
  theta <- model$theta[o,t]
  fitdata <- data.frame(list(x = years, y = theta))
  booted <- boot(fitdata, R = 100, statistic = boot_fn)
  
  ci <- (1 - ci) / 2
  
  conf_top <- apply(booted$t, 2, function(x) quantile(x, 1-ci, na.rm = T))
  conf_bot <- apply(booted$t, 2, function(x) quantile(x, ci, na.rm = T))
  
  return(data.frame(x=years, y=booted$t0, conf_top = conf_top, conf_bot=conf_bot))
}
```


```{r}
N <- 8
sortcond <- exp(stm.100$beta$logbeta[[1]][,vocab=="climat"])
sortcond <- sortcond * exp(stm.100$beta$logbeta[[1]][,vocab=="energi"])
sortcond <- sortcond * exp(stm.100$beta$logbeta[[1]][,vocab=="environment"])
topics <- order(sortcond, decreasing = T)[1:8]
model <- stm.100
labels <- labelTopics(model, topics)
```


```{r}
nrows <- 4 #ceiling(sqrt(N))
ncols <- 2 #floor(sqrt(N))

# png(file = "SampleClimateTopics.png", 
#     width = ncols * 4, height = nrows * 2,
#     units = "in", res = 300)

par(mfrow = c(nrow, ncol))
par(cex = 0.9)
par(mar = c(1,1,0,0), oma = c(4,4,0.5,0.5))
par(mgp = c(2, 0.6, 0))

for (i in 1:N) {

    t <- topics[i]
    
    plotdata <- moving_window(model, t, meta$year, 0.95)
    
    plot(plotdata$x, plotdata$y, 
       xlim = c(1995, 2020), ylim = c(0, 0.05), 
       lwd = 2, col = "darkgrey", type = 'l', 
       xaxt = 'n', yaxt = 'n',
       xlab = "year", ylab = "proportion")

    grid()
    
    pcol <- rgb(0.1,0.3,0.9,0.1)
    
    polygon(
      c(plotdata$x, rev(plotdata$x)),
      c(plotdata$conf_top, rev(plotdata$conf_bot)), 
      col = pcol
      )
    
    
    #abline(v = c(2015,2016), col = "grey60")

    box(col = "grey60")
    
    mtext(str_c("Topic ",t,": "), side = 3, 
          line = -1.5, adj = 0, cex = 1)
    mtext(str_c(labels$prob[t,1:4], collapse = " "), 
          side = 3, line = -2.5, adj = 0, cex = 0.8)
    
    if (i %in% seq(1, N-ncols+1, ncols)) {
            axis(2, 
                 col = "grey40", 
                 col.axis = "grey20", 
                 at = seq(0, 0.05, 0.01),
                 las = 1)
    }
    if (i %in% (N-ncols+1):N) {
            axis(1, 
                 col = "grey40", 
                 col.axis = "grey20", 
                 at = seq(1995, 2020, 1),
                 las = 1)
    }
}

mtext("Year", side = 1, outer = TRUE, cex = 0.8, line = 2.5)
mtext("Estimated topic proportion", side = 2, outer = TRUE, cex = 0.8, line = 2.5)
```


```{r}
climate_topics <- c(9,89,91,21,70,51)
examples <- list()
for (k in climate_topics) {
  examples[str_c("X",k)] <- findThoughts(stm.100, texts = meta$text, n = 1, topics = c(k))$docs[1]
}
write.csv(examples, file = "topicExamples.csv")
```



```{r}
ts <- findThoughts(stm.100, texts = meta$text, n = 1, topics = c(k))


```

